---
title: "Data analysis *Testgenauigkeit Bayes* from exercise session *Stochastik und ind. Statistik* (Master Wirtschaftsinformatik) / May 15 2024"
author: "Markus Konrad"
date: "2024-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation

### Load data, helper functions

```{r, message=FALSE, warning=FALSE}
source("analysis_helpers.R")

tracking_data <- load_app_sessions_tracking_data(c("36263541b9", "e47a7d46bf"), c("treat", "ctrl"))
```

```{r}
track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```

### Limit tracking session events to exercise time frame

```{r}
starttime <- strptime("2024-05-15 13:15", "%Y-%m-%d %H:%M")    # exercise start - 30 min.
endtime <- strptime("2024-05-15 17:30", "%Y-%m-%d %H:%M")      # exercise end + 30 min.    

tracking_data <- filter(tracking_data, event_time >= starttime, event_time <= endtime) |>
    group_by(track_sess_id) |>
    mutate(track_sess_end = min(track_sess_end, max(event_time))) |>
    ungroup() |>
    filter(track_sess_start >= starttime, track_sess_end <= endtime)

track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```

```{r}
plot_tracking_sess_durations(track_sess_times, by_user_code = TRUE)
```

- first user: 2 tabs?
- short user session in middle: lab computer problem
- short user sessions at the end: restart at the end to show something to the instructor
- dismiss short sessions?
- merge 6ab33... and 9cd0...?
- merge f93a... two sessions?

```{r}
plot_tracking_sess_durations_hist(track_sess_times, binwidth = 0.25)
```

- long interaction time

```{r}
median(track_sess_times$duration) |> as.double(units = "mins")
```

### Number of observations, unique users and event types

- many observations

```{r}
dim(tracking_data)
```

- number of unique users:

```{r}
length(unique(tracking_data$user_code))
```

- treatment and control assignments:

```{r}
distinct(tracking_data, user_code, group) |> count(group)
```


- all used a desktop PC

```{r}
group_by(tracking_data, track_sess_id) |>
    distinct(form_factor) |>
    ungroup() |>
    count(form_factor)
```


- number of events per event type:

```{r}
res <- plot_event_type_counts(tracking_data)
res$plot
```


```{r}
res$table
```

- number of events per event type in each tracking session:

```{r, fig.width=9, fig.height=9}
res <- plot_event_type_counts_per_tracking_sess(tracking_data)
res$plot
```


### Question and code exercise submissions

- proportion of correct answers per question:

```{r, fig.width=6, fig.height=8}
quest_data <- question_submit_data(tracking_data)
res <- plot_question_prop_correct(quest_data)
res$plot
```

- number of tries per question:

```{r}
quiz_tries <- question_or_exercise_submit_tries(quest_data)
```

```{r, fig.width=6, fig.height=8}
plot_question_n_tries(quiz_tries)$plot
```

- interestingly, each question was finally answered correctly – no one gave up in between:

```{r}
plot_prop_correct_after_last_try(quiz_tries)
```

```{r}
quiz_prop_correct_per_try <- prop_correct_in_ith_try(quest_data)
plot_prop_correct_per_try(quiz_prop_correct_per_try, "Proportion of correct quiz answers per number of tries")
```


- only a few coding exercises were tried, and even fewer succeeded

```{r}
ex_data <- exercise_result_data(tracking_data)
ex_tries <- question_or_exercise_submit_tries(ex_data)
group_by(ex_tries, ex_label) |>
    summarise(n = n(),
              prop_correct = mean(ex_correct))
```

```{r}
plot_exercise_n_tries(ex_tries)
```


- all in all less then a third of the exercise were answered correctly in the end, means most students gave up

```{r}
mean(ex_tries$ex_correct)
```

```{r}
ex_prop_correct_per_try <- prop_correct_in_ith_try(ex_data)
plot_prop_correct_per_try(ex_prop_correct_per_try, "Proportion of correct code submissions per number of tries")
```

- (on try 6, someone in tracking session #185 made a correct submission and then regressed to a wrong submission afterwards)


- often, the submitted code is not correct R code
- furthermore, students don't understand that the last output is the result but assume that the have to use
  `print(...)` to return the result

```{r}
filter(ex_data, !ex_correct) |>
    pull(value) |>
    trimws() |>
    paste(collapse = "\n---\n") |>
    cat()
```

