---
title: "Data analysis *Testgenauigkeit Bayes* from exercise session *Stochastik und ind. Statistik* (Master Wirtschaftsinformatik) / May 15 2024"
author: "Markus Konrad"
date: "2024-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation

### Load data, helper functions

```{r, message=FALSE, warning=FALSE}
source("analysis_helpers.R")

tracking_data <- load_app_sessions_tracking_data(c("36263541b9", "e47a7d46bf"), c("treat", "ctrl"))
```

```{r}
track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```

### Limit tracking session events to exercise time frame

```{r}
# conversion to the right timezone is extremely important!
# all times in `tracking_data` are in UTC (aka GMT)
starttime <- ymd_hm("2024-05-15 11:55", tz = "UTC")
endtime <- ymd_hm("2024-05-15 15:00", tz = "UTC")

tracking_data <- filter(tracking_data, track_sess_start >= starttime, event_time >= starttime, event_time <= endtime) |>
    group_by(track_sess_id) |>
    mutate(track_sess_end = min(track_sess_end, max(event_time))) |>
    ungroup()

track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```

```{r}
plot_tracking_sess_durations(track_sess_times, by_user_code = TRUE)
```

- first user: 2 tabs?
- short user session in middle: lab computer problem
- short user sessions at the end: restart at the end to show something to the instructor
- dismiss short sessions?
- merge 6ab33... and 9cd0...?
- merge f93a... two sessions?


```{r}
tracking_data <- filter(tracking_data, !(user_code %in% c("13d48be01652b32e", "1e8e8090e4bc1355", "9cd0199df2050778")))
track_sess_times <- tracking_sess_times(tracking_data)
```


```{r}
plot_tracking_sess_durations(track_sess_times, by_user_code = TRUE)
```


```{r}
plot_tracking_sess_durations_hist(track_sess_times, binwidth = 0.25)
```

- long interaction time

```{r}
median(track_sess_times$duration) |> as.double(units = "mins")
```

### Number of observations, unique users and event types

- many observations

```{r}
dim(tracking_data)
```

- number of unique users:

```{r}
length(unique(tracking_data$user_code))
```

- treatment and control assignments:

```{r}
distinct(tracking_data, user_code, group) |> count(group)
```


- all used a desktop PC

```{r}
group_by(tracking_data, track_sess_id) |>
    distinct(form_factor) |>
    ungroup() |>
    count(form_factor)
```


- number of events per event type:

```{r}
res <- plot_event_type_counts(tracking_data)
res$plot
```


```{r}
res$table
```

- number of events per event type per user:

```{r, fig.width=9, fig.height=9}
res <- plot_event_type_counts_per_user(tracking_data)
res$plot
```


### Question and code exercise submissions

- proportion of correct answers per question:

```{r, fig.width=6, fig.height=8}
quest_data <- question_submit_data(tracking_data)
res <- plot_question_prop_correct(quest_data)
res$plot
```

```{r}
res <- plot_question_prop_correct(quest_data, per_group = TRUE)
res$plot
```


- number of tries per question:

```{r}
quiz_tries <- question_or_exercise_submit_tries(quest_data)
```

```{r, fig.width=6, fig.height=8}
plot_question_n_tries(quiz_tries)$plot
```

```{r}
plot_question_n_tries(quiz_tries, per_group = TRUE)$plot
```


```{r}
plot_prop_correct_after_last_try(quiz_tries)
```

```{r}
quiz_prop_correct_per_try <- prop_correct_in_ith_try(quest_data)
plot_prop_correct_per_try(quiz_prop_correct_per_try, "Proportion of correct quiz answers per number of tries")
```


- only a few coding exercises were tried, and even fewer succeeded
- after some tries, there as problem on the server preventing doing any more code exercises
- the submitted code was correct but due to the server problem, it was accepted as correct code
- **hence, all data regarding the coding exercises should be dismissed**

```{r}
ex_data <- exercise_result_data(tracking_data)
ex_tries <- question_or_exercise_submit_tries(ex_data)
group_by(ex_tries, group, ex_label) |>
    summarise(n = n(),
              prop_correct = mean(ex_correct))
```

```{r}
plot_exercise_n_tries(ex_tries)
```


```{r}
ex_prop_correct_per_try <- prop_correct_in_ith_try(ex_data)
plot_prop_correct_per_try(ex_prop_correct_per_try, "Proportion of correct code submissions per number of tries")
```

- as it turns out, the submitted code was correct but due to the server problem, it was accepted as correct code:

```{r}
filter(ex_data, !ex_correct) |>
    pull(value) |>
    trimws() |>
    paste(collapse = "\n---\n") |>
    cat()
```

### Survey

```{r}
survey <- survey_data(tracking_data)

plot_survey_numerical_items(survey)
```

```{r}
multiple_tabs_data <- select(survey, -c(schwierigkeit:kommentar), mehrere_tabs) |>
    mutate(mehrere_tabs = mehrere_tabs == "j") |>
    group_by(group) |>
    summarise(yes = sum(mehrere_tabs),
              no = n() - yes,
              prop = mean(mehrere_tabs),
              se = sqrt(prop * (1-prop) / n()))
multiple_tabs_data
```

```{r}
ggplot(multiple_tabs_data, aes(y = group)) +
    geom_pointrange(aes(xmin = prop - se, x = prop, xmax = prop + se)) +
    scale_x_continuous(limits = c(0, 1)) +
    scale_y_discrete(limits = rev) +
    labs(title = "Proportion of users that opened several tabs according to the survey",
         x = "Proportion and standard error",
         y = "Group")
```

Suggestions for improvements:

```{r}
filter(survey, group == "ctrl", !is.na(kommentar)) |> pull(kommentar)
```

```{r}
filter(survey, group == "treat", !is.na(kommentar)) |> pull(kommentar)
```
