---
title: "Data analysis *Testgenauigkeit Bayes* from exercise session *Stochastik und ind. Statistik* (Master Wirtschaftsinformatik) / Nov 15 2023"
author: "Markus Konrad"
date: "2023-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation

### Load data, helper functions

```{r, message=FALSE}
source("analysis_helpers.R")

tracking_data <- readRDS("data/prepared/f33ac92fb8_tracking_data.rds")
```


### Tracking session duration

```{r}
track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```

### Limit tracking session events to exercise time frame

```{r}
starttime <- strptime("2023-11-15 13:15", "%Y-%m-%d %H:%M")    # exercise start - 30 min.
endtime <- strptime("2023-11-15 17:30", "%Y-%m-%d %H:%M")      # exercise end + 30 min.    

tracking_data <- filter(tracking_data, event_time >= starttime, event_time <= endtime) |>
    group_by(track_sess_id) |>
    mutate(track_sess_start = min(track_sess_start, min(event_time)),
           track_sess_end = min(track_sess_end, max(event_time))) |>
    ungroup()

track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```

```{r}
plot_tracking_sess_durations_hist(track_sess_times, binwidth = 0.25)
```

- long interaction time

```{r}
median(track_sess_times$duration) |> as.double(units = "mins")
```

### Number of observations, unique users and event types

- many observations

```{r}
dim(tracking_data)
```

- number of unique users:

```{r}
length(unique(tracking_data$user_app_sess_code))
```

- each user created only one tracking session:

```{r}
length(unique(tracking_data$track_sess_id))
```

- one user used a tablet, all others a laptop or desktop PC:

```{r}
group_by(tracking_data, track_sess_id) |>
    distinct(form_factor) |>
    ungroup() |>
    count(form_factor)
```


- number of events per event type:

```{r}
res <- plot_event_type_counts(tracking_data)
res$plot
```


```{r}
res <- plot_event_type_counts(tracking_data)
res$table
```

- number of events per event type in each tracking session:

```{r, fig.width=9, fig.height=9}
res <- plot_event_type_counts_per_tracking_sess(tracking_data)
res$plot
```

- some students apparently did not submit code exercises, but all submitted answers on questions


```{r}
submit_event_counts <- filter(res$table, type %in% c("ex_result", "ex_submit", "question_submit")) |>
    pivot_wider(names_from = type, values_from = n, values_fill = 0)
submit_event_counts    
```

```{r}
mutate(submit_event_counts, ex = ex_result + ex_submit) |>
    select(-c(ex_result, ex_submit)) |>
    filter(question_submit == 0 | ex == 0)
```

### Question and code exercise submissions

- proportion of correct answers per question:

```{r}
quest_data <- question_submit_data(tracking_data)
res <- plot_question_prop_correct(quest_data)
res$plot
```

```{r}
res$table
```

- number of tries per question:

```{r}
quiz_tries <- question_or_exercise_submit_tries(quest_data)
```

```{r}
plot_question_n_tries(quiz_tries)
```

- interestingly, each question was finally answered correctly – no one gave up in between:

```{r}
all(quiz_tries$ex_correct)
```

```{r}
quiz_prop_correct_per_try <- prop_correct_in_ith_try(quest_data)
plot_prop_correct_per_try(quiz_prop_correct_per_try, "Proportion of correct quiz answers per number of tries")
```


- only a few coding exercises were tried, and even fewer succeeded

```{r}
ex_data <- exercise_result_data(tracking_data)
ex_tries <- question_or_exercise_submit_tries(ex_data)
group_by(ex_tries, ex_label) |>
    summarise(n = n(),
              prop_correct = mean(ex_correct))
```

```{r}
plot_exercise_n_tries(ex_tries)
```


- all in all less then a third of the exercise were answered correctly in the end, means most students gave up

```{r}
mean(ex_tries$ex_correct)
```

```{r}
ex_prop_correct_per_try <- prop_correct_in_ith_try(ex_data)
plot_prop_correct_per_try(ex_prop_correct_per_try, "Proportion of correct code submissions per number of tries")
```

- (on try 6, someone in tracking session #185 made a correct submission and then regressed to a wrong submission afterwards)


- often, the submitted code is not correct R code
- furthermore, students don't understand that the last output is the result but assume that the have to use
  `print(...)` to return the result

```{r}
filter(ex_data, !ex_correct) |>
    pull(value) |>
    trimws() |>
    paste(collapse = "\n---\n") |>
    cat()
```


### Mouse tracks


```{r, fig.width=9, fig.height=5}
tracks_features <- list()

for (track_sess_id in sort(unique(tracking_data$track_sess_id))) {
    mouse_tracks_data <- mouse_tracks_for_tracking_sess(tracking_data, track_sess_id)
    form_factor <- mouse_tracks_data$form_factor
    mouse_tracks_data <- mouse_tracks_data$tracks
    
    tracksess_tracks_features <- mouse_tracks_features(mouse_tracks_data)
    tracksess_tracks_features$track_sess_id <- track_sess_id
    tracksess_tracks_features$form_factor <- form_factor
    tracks_features[[track_sess_id]] <- tracksess_tracks_features
    
    print(plot_mouse_tracks_for_tracking_session(mouse_tracks_data, track_sess_id, form_factor,
                                                 x_limits = c(0, 1),
                                                 y_limits= c(1.5, 0)))
}
```


```{r}
tracks_features_per_track_sess <- bind_rows(tracks_features) |>
    arrange(track_sess_id, t_step)

tracks_features_per_track_sess_filled <-
    expand.grid(track_sess_id = sort(unique(tracks_features_per_track_sess$track_sess_id)),
            t_step = 1:max(tracks_features_per_track_sess$t_step)) |>
    left_join(tracks_features_per_track_sess, c('track_sess_id', 't_step')) |>
    arrange(track_sess_id, t_step) |>
    mutate(mean_t_step_V = ifelse(is.na(mean_t_step_V), 0, mean_t_step_V)) |>
    fill(form_factor)
```

```{r}
plot_mouse_velocity_heatmap(tracks_features_per_track_sess_filled)
```


```{r}
filter(tracks_features_per_track_sess_filled, t_step <= 10) |>
    plot_mouse_velocity_heatmap()
```

