---
title: "Data analysis *Testgenauigkeit Bayes* from exercise session *Stochastik und ind. Statistik* (Master Wirtschaftsinformatik) / Nov 15 2023 - additional visualizations"
author: "Markus Konrad, Andre Beinrucker"
date: "2023-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation
- this documents contains supplementary visualisations using plotly graphs, to visualise the quantity and timeline of the quiz answers

### Load data, helper functions

```{r, message=FALSE}
source("analysis_helpers.R")
library(lubridate)
library(forcats) #zum neu Ordnen der Faktor-levels ex_label mit fct_relevel()
library(plotly)
library(htmltools)#to plot a series of plotly graphs through a for loop, see https://forum.posit.co/t/display-plotly-graph-produced-in-a-for-loop-in-rmakrdown-html/168188
#tracking_data <- readRDS("data/prepared/f33ac92fb8_tracking_data.rds")
tracking_data <- load_app_sessions_tracking_data(c("f33ac92fb8"))
```


### Tracking session duration

```{r include=FALSE}
track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)

```

### Limit tracking session events to exercise time frame

```{r include=FALSE}
starttime <- strptime("2023-11-15 13:15", "%Y-%m-%d %H:%M")    # exercise start - 30 min.
endtime <- strptime("2023-11-15 17:30", "%Y-%m-%d %H:%M")      # exercise end + 30 min.    

tracking_data <- filter(tracking_data, event_time >= starttime, event_time <= endtime) |>
    group_by(user_code) |>
    mutate(track_sess_start = min(track_sess_start, min(event_time)),
           track_sess_end = min(track_sess_end, max(event_time))) |>
    ungroup()

track_sess_times <- tracking_sess_times(tracking_data)

plot_tracking_sess_durations(track_sess_times)
```


```{r}
tracking_data <- filter(tracking_data, !(user_code %in% c("13d48be01652b32e", "1e8e8090e4bc1355", "9cd0199df2050778")))
quest_data <- question_submit_data(tracking_data)
```


### Plot user ID vs. time of question submission (one graph for each question)

```{r results='asis'}
plot_submission_times_questions(loop_over = quo(ex_label),
                                loop_over_list = unique(quest_data$ex_label),
                                group_by_variable = quo(user_code),
                                quest_data=quest_data)
#knitting this document gives the desired plotly graphs, executing the codechunk wise additionally outputs some strange shiny.tag.list 
```
### Plot question vs. time of question submission  (one graph for each student)

```{r results='asis'}
plot_submission_times_questions(loop_over = quo(user_code),
                                loop_over_list = unique(quest_data$user_code),
                                group_by_variable = quo(ex_label),
                                quest_data=quest_data)
#knitting this document gives the desired plotly graphs, executing the code chunkwise additionally outputs some strange shiny.tag.list 
```

