---
title: "Data analysis *Testgenauigkeit Bayes* from exercise session *Stochastik und ind. Statistik* (Master Wirtschaftsinformatik) / May 15 2024 - additional visualizations"
author: "Markus Konrad, Andre Beinrucker"
date: "2024-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation
- this documents contains supplementary visualisations using plotly graphs, to visualise the quantity and timeline of the quiz answers

### Load data, helper functions

```{r, message=FALSE, warning=FALSE}
source("analysis_helpers.R")
library(lubridate)
library(plotly)
library(htmltools)#to plot a series of plotly graphs through a for loop, see https://forum.posit.co/t/display-plotly-graph-produced-in-a-for-loop-in-rmakrdown-html/168188

QUIZ_QUESTIONS_ORDER <- ordered(c(
    "clinicalstudy1",
    "clinicalstudy2",
    "calc_sens",
    "calc_spec",
    "confmat",
    "P_T_K",
    "P_K",
    "P_T",
    "P_K_T",
    "P_K_T_vergleich",
    "P_nK_nT_ausdruck",
    "P_nK_nT_berechnet",
    "ppv_sens"
))

tracking_data <- load_app_sessions_tracking_data(c("36263541b9", "e47a7d46bf"), c("treat", "ctrl"))
```

```{r}
track_sess_times <- tracking_sess_times(tracking_data)
#plot_tracking_sess_durations(track_sess_times)
```

### Limit tracking session events to exercise time frame

```{r}
# conversion to the right timezone is extremely important!
# all times in `tracking_data` are in UTC (aka GMT)
starttime <- ymd_hm("2024-05-15 11:55", tz = "UTC")
endtime <- ymd_hm("2024-05-15 15:00", tz = "UTC")

tracking_data <- filter(tracking_data, track_sess_start >= starttime, event_time >= starttime, event_time <= endtime) |>
    group_by(track_sess_id) |>
    mutate(track_sess_end = min(track_sess_end, max(event_time))) |>
    ungroup()

track_sess_times <- tracking_sess_times(tracking_data)
plot_tracking_sess_durations(track_sess_times)
```

```{r}
plot_tracking_sess_durations(track_sess_times, by_user_code = TRUE)
```

- first user: 2 tabs?
- short user session in middle: lab computer problem
- short user sessions at the end: restart at the end to show something to the instructor
- dismiss short sessions?
- merge 6ab33... and 9cd0...?
- merge f93a... two sessions?


```{r}
tracking_data <- filter(tracking_data, !(user_code %in% c("13d48be01652b32e", "1e8e8090e4bc1355", "9cd0199df2050778")))
track_sess_times <- tracking_sess_times(tracking_data)
```

```{r include=FALSE}
quest_data <- question_submit_data(tracking_data, QUIZ_QUESTIONS_ORDER)
res <- plot_question_prop_correct(quest_data)
res$plot
```


### Plot user ID vs. time of question submission (one graph for each question)

```{r results='asis'}
plot_submission_times_questions(loop_over = quo(ex_label),
                                loop_over_list = unique(quest_data$ex_label),
                                group_by_variable = quo(user_code),
                                quest_data=quest_data)
#knitting this document gives the desired plotly graphs, executing the codechunk wise additionally outputs some strange shiny.tag.list 
```
### Plot question vs. time of question submission  (one graph for each student)

```{r results='asis'}
plot_submission_times_questions(loop_over = quo(user_code),
                                loop_over_list = unique(quest_data$user_code),
                                group_by_variable = quo(ex_label),
                                quest_data=quest_data)
#knitting this document gives the desired plotly graphs, executing the code chunkwise additionally outputs some strange shiny.tag.list 
```


